\vspace{-2cm} The effects of transitions of power on the contents of municipal government websites

### 2017-07-26 paper/manuscript.tex
more analysis of topic weights + writeup

@@

@@

>>>>

Topics for which there are stark differences in their distribution across documents between Democrats and Republicans are of particular interest to us. To detect these topics, we take the absolute difference of the median document topic weights, and arrange them as a histogram, see figure \ref{diffsize}. For the most part, differences are small. For a few topics however, a contrasts emerges.

%size of the differences
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{diffsize}
	\includegraphics[width=\linewidth]{figures/diffsize.pdf}
\end{figure}

Figure \ref{plotWTP_bigdiffs} displays the word-topic probabilities for the 10 topics with the largest partisan differences. Some of these, such as topic 82, with its focus on policing, safety and crime could be construed as politically charged. For the most part however, these topics focus on administrative matters.

@@

To further investigate the topics with large partisan differences, figure \ref{plotWTP_bigdiffs} shows densities of topic weights just like figure \ref{doctopics_density}, but reduced to only the topics with the largest differences. It appears that mere absolute differences between the medians (or some other measure of central tendency) obscures the fact that the distributions themselves are quite different.

@@

To further investigate this issue, we look at the raw data itself - the document-topic matrices for Democrats and Republicans, displayed as heatmaps. Figure \ref{heatmaps_weights} shows that especially for Republicans (but also for Democrats, to a lesser extent), there appears to be extensive clustering for consecutive documents. Since the order of the documents in the corpus is dependent on the cities in which they appear in, it seems that topics are mere representation of city websites - each website `owns' a number of topics, that appear across all of its documents, and hardly anywhere else. One possible cause for this type of clustering is the fact that documents frequently share common words, for example pertaining to navigation on the site, or standard forms that are shared throughout all documents.

%Heatmaps
\begin{figure}[!ht]
	\centering % Using \begin{figure*} makes the figure take up the entire width of the page
	\caption{Word-topic probabilities for topics with big partisan differences}
	\label{heatmaps_weights}
	\includegraphics[width=\linewidth]{figures/heatmaps_weights.png}
\end{figure}
